---
title: "Spatial Analysis in children referals"
author: "Gregory Biland, Oliver Grübner, Michael von Rhein"
output:
  html_document:
    highlight: textmate
    number_sections: true
    theme: journal
    toc: true
    toc_float: true
  word_document:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
```

```{r message=FALSE, warning=FALSE, include=FALSE}
library(dplyr)
library(tidyverse)
library(sf)
library(lubridate)
library(ggplot2)
library(gridExtra)
library(grid)
library(spdep)
library(readxl)
library(classInt)
library(stats)
library(ggspatial)
library(tmap)
library(MASS)

```

```{r message=FALSE, warning=FALSE, include=FALSE}
Zurich <- st_read("Data/Data_Zurich/Data_Zurich_PLZ_UC.gpkg")
Bellinzona <- st_read("Data/Data_Bellinzona/Data_Bellinzona_PLZ_UC.gpkg")
Geneva <- st_read("Data/Data_Geneva/Data_Geneva_PLZ_UC.gpkg")

Zurich_Distance <- read_csv("Data/Data_Zurich/Zurich_Distances.csv")
Geneva_Distance <- read_csv("Data/Data_Geneva/Geneva_Distances.csv")
Bellinzona_Distance <- read_csv("Data/Data_Bellinzona/Bellinzona_Distances.csv")

# Load Canton and ZIP code borders
canton_borders <- st_read("Data/Geodaten/Kantonsgrenzen/Kantonsgrenzen.shp")
zipcode_borders <- st_read("Data/Geodaten/PLZ/PLZ.geojson")
traffic_areas <- st_read("Data/Geodaten/Verkehrszonen_Schweiz_NPVM_2017/Verkehrszonen_Schweiz_NPVM_2017.gpkg")
lakes <- st_read("Data/Geodaten/aqua.shp")

# Remove rows with NA values
Zurich <- na.omit(Zurich)%>% 
  mutate(ID = row_number()) %>% filter(Age <= 18)
Bellinzona <- na.omit(Bellinzona)%>% 
  mutate(ID = row_number()) %>% filter(Age <= 18)
Geneva <- na.omit(Geneva) %>% 
  mutate(ID = row_number()) %>% filter(Age <= 18)

## Cordinates Hospitals

zurich_coords <- c(2684474.6, 1247415.3)
bellinzona_coords <- c(2722573.5, 1115952.8)
geneva_coords <- c(2500343.9, 1116296.7)

```

```{r message=FALSE, warning=FALSE, include=FALSE}
# Convert zipcode_borders sf object to data frame and remove geometry column
zipcode_borders_df <- st_set_geometry(zipcode_borders, NULL) %>% as.data.frame()

# Perform left joins
Zurich_joined <- Zurich_Distance %>%
  left_join(zipcode_borders_df, by = c("Zipcode" = "PLZ")) %>% drop_na(Distance, Sum)

Bellinzona_joined <- Bellinzona_Distance %>%
  left_join(zipcode_borders_df, by = c("Zipcode" = "PLZ")) %>% drop_na(Distance, Sum)

Geneva_joined <- Geneva_Distance %>%
  left_join(zipcode_borders_df, by = c("Zipcode" = "PLZ")) %>% drop_na(Distance, Sum)

write_csv(Zurich_joined, "Data/Data_Zurich/Zurich_joined.csv")
write_csv(Bellinzona_joined, "Data/Data_Bellinzona/Bellinzona_joined.csv")
write_csv(Geneva_joined, "Data/Data_Geneva/Geneva_joined.csv")

```

# Background

During the SARS-CoV-2 pandemic, the emergency wards of the three children's hospitals in the Geneva area (French-speaking Switzerland), Bellinzona (Ticino) and Zurich (German-speaking Switzerland) were very busy. The closure, ordered by the authorities, led to a reduction of up to 35% in the number of consultations per month.

This initial decrease was followed by a gradual increase in the number of cases, which returned to the initial level after about a year and even showed an increase thereafter. Against this background, we wanted to investigate the following three research questions

-   Were there differences in the characterisation of the cohorts treated in the three parts of the country before, during and after the closure?

-   How did the spatial distribution of children presenting and the catchment area of the three emergency departments change during the pandemic?

-   Which factors were relevant for the decreasing and then increasing utilisation?

# Methods

This paper examines the changes in hospital visits concerning the pandemic in three periods: before the pandemic (March 1, 2018 - March 10, 2020), during the pandemic (March 11, 2020 - March 21, 2021), and after the pandemic (March 22, 2021 - March 1, 2022). 
The children were categorized according to age (0-4, 5-12, 13-18 years) and severity (severe: categories 1-3, mild: 4-5), considering the type of admission, whether outpatient or inpatient. The distinction between cantonal and non-cantonal emergency admissions allowed a differentiated analysis of the figures to identify regional differences and whether the COVID effect differentiates between cantonal and non-cantonal areas. The analysis of travel distances for hospital visits is based on two approaches (Euclidean and distance matrix). For the Euclidean distance (km), the shortest distance was calculated between the geometric centers of the postcode areas and the locations of the hospitals in Geneva, Bellinzona, and Zurich. The second approach uses the Swiss traffic zones, for which a matrix was computed that represents the shortest driving distance (km) between each traffic zone in Switzerland on the Swiss road network. The distances used in this paper are capped at 60km in each case - greater distances were treated as outliers and therefore not included in the analysis. To analyze changes in distances over three time periods, the distances above and below the median of each city were compared to the pre-pandemic period. The median for the first time period was taken and the distribution was calculated, which means finding the proportion of distances above and below this median for all three time periods based on the median of the pre-pandemic period.
Kolmogorov-Smirnov tests were used to statistically analyze the distance variations over three periods to determine significant differences in travel distances. To further identify trends, the mean travel distance was calculated for each hospital location and period for comparison. 
A Poisson regression model was used to determine the influence of variables such as age, gender, and triage category on hospital visits. This was done for each period, hospital, and all three hospitals and periods.

# Results

## Differences in the characterization of the cohorts

### Variable Distribution

```{r}

plotDistributions <- function(data, city_name, normalisation_before, normalisation_during, normalisation_after) {
  
  # Group TriageCategory into two levels
  data$TriageGroup <- ifelse(data$TriageCategory %in% 1:3, "Severe", "Light")
  
  # Create separate datasets for before, during, and after the pandemic
  data_before <- data[data$Date < as.Date("2020-03-11"), ]
  data_during <- data[data$Date >= as.Date("2020-03-11") & data$Date < as.Date("2021-03-22"), ]
  data_after <- data[data$Date >= as.Date("2021-03-22"), ]

  # Plot for Age (Age)
  p1_before <- ggplot(data_before, aes(x = Age)) +
    geom_histogram(aes(y = stat(count / normalisation_before)), binwidth = 1, fill = "#88CCEE", color = "black") +
    labs(title = paste("Before Pandemic"),
         x = "Age", y = "Normalized Count") +
      ylim(0, 1500) +
      theme_minimal()+
      theme(
      plot.title = element_text(size = 11, face = "italic", hjust = 0.5),
      axis.title.x = element_text(size = 8),
      axis.title.y = element_text(size = 8)
    )

  p1_during <- ggplot(data_during, aes(x = Age)) +
    geom_histogram(aes(y = stat(count / normalisation_during)), binwidth = 1, fill = "#CC6677", color = "black") +
    labs(title = paste("During Pandemic"),
         x = "Age", y = "Normalized Count") +
      ylim(0, 1500) +
      theme_minimal()+
      theme(
      plot.title = element_text(size = 11, face = "italic", hjust = 0.5),
      axis.title.x = element_text(size = 8),
      axis.title.y = element_text(size = 8)
    )
  
  p1_after <- ggplot(data_after, aes(x = Age)) +
    geom_histogram(aes(y = stat(count / normalisation_after)), binwidth = 1, fill = "#117733", color = "black") +
    labs(title = paste("After Pandemic"),
         x = "Age", y = "Normalized Count") +
      ylim(0, 1500) +
      theme_minimal()+
      theme(
      plot.title = element_text(size = 11, face = "italic", hjust = 0.5),
      axis.title.x = element_text(size = 8),
      axis.title.y = element_text(size = 8)
    )

  # Plot for Age Groups
  data_before$AgeGroup <- cut(data_before$Age, breaks = c(0, 4, 12, 18), labels = c("0-4", "5-12", "13-18"))
  data_during$AgeGroup <- cut(data_during$Age, breaks = c(0, 4, 12, 18), labels = c("0-4", "5-12", "13-18"))
  data_after$AgeGroup <- cut(data_after$Age, breaks = c(0, 4, 12, 18), labels = c("0-4", "5-12", "13-18"))

  p2_before <- ggplot(data_before, aes(x = AgeGroup)) +
    geom_bar(aes(y = stat(count / normalisation_before)), fill = "#88CCEE", color = "black") +
    labs(title = paste("Before Pandemic"),
         x = "Age Group", y = "Normalized Count") +
      ylim(0, 2500) +
      theme_minimal()+
      theme(
      plot.title = element_text(size = 11, face = "italic", hjust = 0.5),
      axis.title.x = element_text(size = 8),
      axis.title.y = element_text(size = 8)
    )
  
  p2_during <- ggplot(data_during, aes(x = AgeGroup)) +
    geom_bar(aes(y = stat(count / normalisation_during)), fill = "#CC6677", color = "black") +
    labs(title = paste("During Pandemic"),
         x = "Age Group", y = "Normalized Count") +
      ylim(0, 2500) +
      theme_minimal()+
      theme(
      plot.title = element_text(size = 11, face = "italic", hjust = 0.5),
      axis.title.x = element_text(size = 8),
      axis.title.y = element_text(size = 8)
    )

  p2_after <- ggplot(data_after, aes(x = AgeGroup)) +
    geom_bar(aes(y = stat(count / normalisation_after)), fill = "#117733", color = "black") +
    labs(title = paste("After Pandemic"),
         x = "Age Group", y = "Normalized Count") +
      ylim(0, 2500) +
      theme_minimal()+
      theme(
      plot.title = element_text(size = 11, face = "italic", hjust = 0.5),
      axis.title.x = element_text(size = 8),
      axis.title.y = element_text(size = 8)
    )

  # Plot for TriageCategory
  p3_before <- ggplot(data_before, aes(x = TriageCategory)) +
    geom_bar(aes(y = stat(count / normalisation_before)), fill = "#88CCEE", color = "black") +
    labs(title = paste("Before Pandemic"),
         x = "Triage category", y = "Normalized Count") +
      ylim(0, 2000) +
      theme_minimal()+
      theme(
      plot.title = element_text(size = 11, face = "italic", hjust = 0.5),
      axis.title.x = element_text(size = 8),
      axis.title.y = element_text(size = 8)
    )
  
  p3_during <- ggplot(data_during, aes(x = TriageCategory)) +
    geom_bar(aes(y = stat(count / normalisation_during)), fill = "#CC6677", color = "black") +
    labs(title = paste("During Pandemic"),
         x = "Triage category", y = "Normalized Count") +
      ylim(0, 2000) +
      theme_minimal()+
      theme(
      plot.title = element_text(size = 11, face = "italic", hjust = 0.5),
      axis.title.x = element_text(size = 8),
      axis.title.y = element_text(size = 8)
    )
  
  p3_after <- ggplot(data_after, aes(x = TriageCategory)) +
    geom_bar(aes(y = stat(count / normalisation_after)), fill = "#117733", color = "black") +
    labs(title = paste("After Pandemic"),
         x = "Triage category", y = "Normalized Count") +
      ylim(0, 2000) +
      theme_minimal()+
      theme(
      plot.title = element_text(size = 11, face = "italic", hjust = 0.5),
      axis.title.x = element_text(size = 8),
      axis.title.y = element_text(size = 8)
    )

  # Plot for TriageGroup (Severity)
  p4_before <- ggplot(data_before, aes(x = TriageGroup)) +
    geom_bar(aes(y = stat(count / normalisation_before)), fill = "#88CCEE", color = "black") +
    labs(title = paste("Before Pandemic"),
         x = "Severity", y = "Normalized Count") +
      ylim(0, 2500) +
      theme_minimal()+
      theme(
      plot.title = element_text(size = 11, face = "italic", hjust = 0.5),
      axis.title.x = element_text(size = 8),
      axis.title.y = element_text(size = 8)
    )

  p4_during <- ggplot(data_during, aes(x = TriageGroup)) +
    geom_bar(aes(y = stat(count / normalisation_during)), fill = "#CC6677", color = "black") +
    labs(title = paste("During Pandemic"),
         x = "Severity", y = "Normalized Count") +
      ylim(0, 2500) +
      theme_minimal()+
      theme(
      plot.title = element_text(size = 11, face = "italic", hjust = 0.5),
      axis.title.x = element_text(size = 8),
      axis.title.y = element_text(size = 8)
    )
  
  p4_after <- ggplot(data_after, aes(x = TriageGroup)) +
    geom_bar(aes(y = stat(count / normalisation_after)), fill = "#117733", color = "black") +
    labs(title = paste("After Pandemic"),
         x = "Severity", y = "Normalized Count") +
    theme_minimal() +
      ylim(0, 2500) +
      theme(
      plot.title = element_text(size = 11, face = "italic", hjust = 0.5),
      axis.title.x = element_text(size = 8),
      axis.title.y = element_text(size = 8)
    )

  # Combine the plots using grid.arrange
  age_distribution <- grid.arrange(p1_before, p1_during, p1_after,ncol = 3,
                                   top = textGrob(paste(city_name, "Age Distribution"), 
                                                  gp = gpar(fontsize = 16)))
  
  age_group_distribution <- grid.arrange(p2_before, p2_during, p2_after, ncol = 3,
                                         top = textGrob(paste(city_name, "Age Group Distribution"), 
                                                        gp = gpar(fontsize = 16)))
  
  triage_distribution <- grid.arrange(p3_before, p3_during, p3_after, ncol = 3,
                                         top = textGrob(paste(city_name, "Triage Distribution"), 
                                                        gp = gpar(fontsize = 16)))
  
  triage_severity_distribution <- grid.arrange(p4_before, p4_during, p4_after, ncol = 3,
                                         top = textGrob(paste(city_name, "Triage Severity Distribution"), 
                                                        gp = gpar(fontsize = 16)))
  
  return(list(age_distribution = age_distribution, 
              age_group_distribution = age_group_distribution,
              triage_distribution = triage_distribution,
              triage_severity_distribution = triage_severity_distribution))
}

normalisation_before <- 24.32
normalisation_during <- 12.35
normalisation_after <- 11.21

zurich_plots <- plotDistributions(Zurich, "Zurich", normalisation_before, normalisation_during, normalisation_after)
bellinzona_plots <- plotDistributions(Bellinzona, "Bellinzona", normalisation_before, normalisation_during, normalisation_after)
geneva_plots <- plotDistributions(Geneva, "Geneva", normalisation_before, normalisation_during, normalisation_after)


```

### Hospitalization Rates

```{r}
TypeDistributions <- function(data, city_name) {
  # Split data based on time periods
  df_before <- data[data$Date < as.Date("2020-03-11"), ]
  df_during <- data[data$Date >= as.Date("2020-03-11") & data$Date < as.Date("2021-03-22"), ]
  df_after <- data[data$Date >= as.Date("2021-03-22"), ]

  # Plotting function
  make_plot <- function(data,title_color, normalisation, title) {
    ggplot(data, aes(x = Type)) +
      geom_bar(aes(y = stat(count / normalisation)), fill = title_color, color = "black") +
      labs(title = title,
           x = "Type", y = "Normalized Count") +
      ylim(0, 3500) +
      theme_minimal()+
      theme(
      plot.title = element_text(size = 11, face = "italic", hjust = 0.5),
      axis.title.x = element_text(size = 8),
      axis.title.y = element_text(size = 8)
    )
  }
  
  # Create plots for each period
  title_before <- "Before Pandemic"
  title_during <- "During Pandemic"
  title_after <- "After Pandemic"

  # Create plots using specified colors
  plot_before <- make_plot(df_before, "#88CCEE", 24.32, title_before)
  plot_during <- make_plot(df_during, "#CC6677", 12.35, title_during)
  plot_after <- make_plot(df_after, "#117733", 11.21, title_after)

  # Combine plots
  combined_plot <- grid.arrange(plot_before, plot_during, plot_after, ncol = 3,
                                         top = textGrob(paste(city_name, "Hospitalization Type Distribution"), 
                                                        gp = gpar(fontsize = 16)))

  return(combined_plot)
}

# Apply the function for each city
TypeDistributions(Geneva, "Geneva")
TypeDistributions(Zurich, "Zurich")
TypeDistributions(Bellinzona, "Bellinzona")
```

### Cantonal Visitations

```{r echo=FALSE, message=FALSE, warning=FALSE}

plotVisitationsByCanton <- function(data, canton, city_name) {
  # Separate data into three periods
  data_before <- data[data$Date < as.Date("2020-03-11"), ]
  data_during <- data[data$Date >= as.Date("2020-03-11") & data$Date < as.Date("2021-03-22"), ]
  data_after <- data[data$Date >= as.Date("2021-03-22"), ]
  
  # Count Visitations by canton
  count_kanton <- function(df, canton) {
    kanton_count <- sum(df$Canton == canton, na.rm = TRUE)
    other_count <- nrow(df) - kanton_count
    return(data.frame(Canton = factor(c("Other", canton), levels = c("Other", canton)), 
                      Count = c(other_count, kanton_count)))
  }

  # Calculate counts for each period
  counts_before <- count_kanton(data_before, canton)
  counts_during <- count_kanton(data_during, canton)
  counts_after <- count_kanton(data_after, canton)

  # Create plots
  plot_counts <- function(counts, normalisation, title) {
    ggplot(counts, aes(x = Canton, y = Count/normalisation, fill = Canton)) +
      geom_bar(stat = "identity") +
      scale_fill_manual(values = setNames(c("#88CCEE", "#CC6677"), c("Other", canton))) +
      labs(title = title, x = "Canton", y = "Normalized Count") +
      theme_minimal() +
      ylim(0, 3500) +
      theme(legend.position = "none",
            plot.title = element_text(size = 11, face = "italic", hjust = 0.5),
            axis.title.x = element_text(size = 8), 
            axis.title.y = element_text(size = 8)
      )
  }

  # Create plots for each period
  title_before <- "Before Pandemic"
  title_during <- "During Pandemic"
  title_after <- "After Pandemic"
  
  plot_before <- plot_counts(counts_before, 24.32, title_before)
  plot_during <- plot_counts(counts_during, 12.35, title_during)
  plot_after <- plot_counts(counts_after, 11.21, title_after)
  
  # Combine the plots side by side using grid.arrange from gridExtra package
  combined_plot <- gridExtra::grid.arrange(plot_before, plot_during, plot_after, ncol = 3,
                                         top = textGrob(paste(city_name, "Cantonal Visitation Distribution"), 
                                                        gp = gpar(fontsize = 16)))
  
  return(combined_plot)
}

# Test with sample data frames and kanton. 
# Make sure Zurich data frame is correctly defined and loaded before running this.
plotVisitationsByCanton(Zurich, "ZH", "Zurich")
plotVisitationsByCanton(Bellinzona, "TI", "Bellinzona")  
plotVisitationsByCanton(Geneva, "GE", "Geneva")


```

### Distance Computation

#### Calculated Distances (Euclidean)

```{r echo=FALSE, message=FALSE, warning=FALSE}

calculateMinDistances <- function(data, coords) {
  # Separate data into three periods
  data_before <- data[data$Date < as.Date("2020-03-11"), ]
  data_during <- data[data$Date >= as.Date("2020-03-11") & data$Date < as.Date("2021-03-22"), ]
  data_after <- data[data$Date >= as.Date("2021-03-22"), ]
  
  # Internal function to calculate distances
  calcDist <- function(df, coords) {
    hospital <- st_sfc(st_point(coords), crs = st_crs(df))
    distances <- st_distance(df, hospital)
    distances <- as.vector(matrix(distances, ncol = 1))
    return(distances[distances <= 60000])  # Filter out distances > 75km
  }
  
  # Calculate distances for each period
  distances_before <- calcDist(data_before, coords)
  distances_during <- calcDist(data_during, coords)
  distances_after <- calcDist(data_after, coords)
  
  return(list(before = distances_before, during = distances_during, after = distances_after))
}

zurich_distances <- calculateMinDistances(Zurich, zurich_coords)
bellinzona_distances <- calculateMinDistances(Bellinzona, bellinzona_coords)
geneva_distances <- calculateMinDistances(Geneva, geneva_coords)

plotDistanceDistribution <- function(distances, city_name) {
  # Data for each period
  df_before <- data.frame(Distance = distances$before / 1000)  # Convert to kilometers
  df_during <- data.frame(Distance = distances$during / 1000)  
  df_after <- data.frame(Distance = distances$after / 1000)  

  # Calculate the max count for consistent y-axis
  max_count <- max(
    c(
      ggplot_build(ggplot(df_before, aes(x = Distance)) +
                     geom_histogram(binwidth = 1))$data[[1]]$count,
      ggplot_build(ggplot(df_during, aes(x = Distance)) +
                     geom_histogram(binwidth = 1))$data[[1]]$count,
      ggplot_build(ggplot(df_after, aes(x = Distance)) +
                     geom_histogram(binwidth = 1))$data[[1]]$count
    )
  )

  # Plot for before pandemic
  plot_before <- ggplot(df_before, aes(x = Distance)) +
    geom_histogram(binwidth = 1.5, fill = "#88CCEE", color = "black") +
    labs(title = paste("Before Pandemic"),
         x = "Distance (km)", y = "Count") +
    ylim(0, max_count) +
    theme_minimal()+
    theme(
      plot.title = element_text(size = 11, face = "italic", hjust = 0.5),
      axis.title.x = element_text(size = 8),
      axis.title.y = element_text(size = 8)
    )

  # Plot for during pandemic
  plot_during <- ggplot(df_during, aes(x = Distance)) +
    geom_histogram(binwidth = 1.5, fill = "#CC6677", color = "black") +
    labs(title = paste("During Pandemic"),
         x = "Distance (km)", y = "Count") +
    ylim(0, max_count) +
    theme_minimal()+
    theme(
      plot.title = element_text(size = 11, face = "italic", hjust = 0.5),
      axis.title.x = element_text(size = 8),
      axis.title.y = element_text(size = 8)
    )

  # Plot for after pandemic
  plot_after <- ggplot(df_after, aes(x = Distance)) +
    geom_histogram(binwidth = 1.5, fill = "#117733", color = "black") +
    labs(title = paste("After Pandemic"),
         x = "Distance (km)", y = "Count") +
    ylim(0, max_count) +
    theme_minimal()+
    theme(
      plot.title = element_text(size = 11, face = "italic", hjust = 0.5),
      axis.title.x = element_text(size = 8),
      axis.title.y = element_text(size = 8)
    )

  # Combine the plots side by side using grid.arrange
  combined_plot <- grid.arrange(plot_before, plot_during, plot_after, ncol = 3,
                                         top = textGrob(paste(city_name, "Distance Distribution"), 
                                                        gp = gpar(fontsize = 16)))

  return(combined_plot)
}


# Generate the plots for each city
zurich_plot <- plotDistanceDistribution(zurich_distances, "Zurich")
bellinzona_plot <- plotDistanceDistribution(bellinzona_distances, "Bellinzona")
geneva_plot <- plotDistanceDistribution(geneva_distances, "Geneva")

print(zurich_plot)
print(bellinzona_plot)
print(geneva_plot)

```

#### Calculated Distances (Matrix)

```{r echo=FALSE, message=FALSE, warning=FALSE}
plotDistanceDistribution <- function(data, city_name) {
  # Filter out distances greater than 60km
  data <- data[data$Distance <= 60, ]

  # Split data based on time periods
  df_before <- data[data$Date < as.Date("2020-03-11"), ]
  df_during <- data[data$Date >= as.Date("2020-03-11") & data$Date < as.Date("2021-03-22"), ]
  df_after <- data[data$Date >= as.Date("2021-03-22"), ]

  # Plotting function
  make_plot <- function(data,title_color, normalisation, title) {
    ggplot(data, aes(x = Distance)) +
      geom_histogram(aes(y = stat(count / normalisation)), binwidth = 2, fill = title_color, color = "black") +
      labs(title = title,
           x = "Distance (km)", y = "Normalized Count") +
      ylim(0, 750) +
      theme_minimal()+
      theme(
      plot.title = element_text(size = 11, face = "italic", hjust = 0.5),
      axis.title.x = element_text(size = 8),
      axis.title.y = element_text(size = 8)
    )
  }
  
  # Create plots for each period
  title_before <- "Before Pandemic"
  title_during <- "During Pandemic"
  title_after <- "After Pandemic"

  # Create plots using specified colors
  plot_before <- make_plot(df_before, "#88CCEE", 24.32, title_before)
  plot_during <- make_plot(df_during, "#CC6677", 12.35, title_during)
  plot_after <- make_plot(df_after, "#117733", 11.21, title_after)

  # Combine plots
  combined_plot <- grid.arrange(plot_before, plot_during, plot_after, ncol = 3,
                                         top = textGrob(paste(city_name, "Distance Distribution"), 
                                                        gp = gpar(fontsize = 16)))

  return(combined_plot)
}

# Apply the function for each city
plotDistanceDistribution(Geneva_Distance, "Geneva")
plotDistanceDistribution(Zurich_Distance, "Zurich")
plotDistanceDistribution(Bellinzona_Distance, "Bellinzona")


```

##### Median Distance Split

```{r echo=FALSE, message=FALSE, warning=FALSE}
plotDistanceDistribution <- function(data, city_name) {

  # Split data based on time periods
  df_before <- data[data$Date < as.Date("2020-03-11"), ]
  df_during <- data[data$Date >= as.Date("2020-03-11") & data$Date < as.Date("2021-03-22"), ]
  df_after <- data[data$Date >= as.Date("2021-03-22"), ]
  
  # Calculate the median from the 'before' period
  median_before <- median(df_before$Distance)
  
  df_before <- df_before[df_before$Distance <= 60, ]
  df_during <- df_during[df_during$Distance <= 60, ]
  df_after <- df_after[df_after$Distance <= 60, ]
  
  # Label distances as 'Below' or 'Above' based on the median
  label_distance <- function(distance) {
    factor(ifelse(distance <= median_before, "Below", "Above"), 
           levels = c("Below", "Above"))
  }
  
  df_before$Proximity <- sapply(df_before$Distance, label_distance)
  df_during$Proximity <- sapply(df_during$Distance, label_distance)
  df_after$Proximity <- sapply(df_after$Distance, label_distance)
  
  # Maximum y-axis value for consistent plotting
  max_Proximity <- max(
    max(table(df_before$Proximity)),
    max(table(df_during$Proximity)),
    max(table(df_after$Proximity))
  )

  # Plotting function
  make_plot <- function(data,title_color, normalisation,title) {
    ggplot(data, aes(x = Proximity, fill = Proximity)) +
      geom_bar(aes(y = stat(count / normalisation)), color = "black") +
      scale_fill_manual(values = c("Below" = "#88CCEE", "Above" = "#CC6677")) +
      labs(title = title,
           x = "Proximity", y = "Normalized Count") +
      theme_minimal() +
      ylim(0, 2000) +
      theme(legend.position = "none",
            plot.title = element_text(size = 11, face = "italic", hjust = 0.5),
            axis.title.x = element_text(size = 8), 
            axis.title.y = element_text(size = 8)
      ) # hjust = 0.5 centers the title
  }
  
  # Create plots for each period
  title_before <- "Before Pandemic"
  title_during <- "During Pandemic"
  title_after <- "After Pandemic"

  # Create plots using specified colors
  plot_before <- make_plot(df_before, "#88CCEE", 24.32, title_before)
  plot_during <- make_plot(df_during, "#CC6677", 12.35, title_during)
  plot_after <- make_plot(df_after, "#117733", 11.21, title_after)

  # Print the median
  print(paste("The median for", city_name ,"is:", median_before))
  
  # Combine plots
  combined_plot <- grid.arrange(plot_before, plot_during, plot_after, ncol = 3,
                                         top = textGrob(paste(city_name, "Median Distance Split Distribution"), 
                                                        gp = gpar(fontsize = 16)))

  return(combined_plot)
}

# Apply the function for each city
plotDistanceDistribution(Geneva_joined, "Geneva")
plotDistanceDistribution(Zurich_joined, "Zurich")
plotDistanceDistribution(Bellinzona_joined, "Bellinzona")

```

```{r}
plotDistanceByCanton <- function(data, kanton, city_name) {
  # Separate data into three periods
  data <- data[data$Distance <= 60, ]
  data_before <- data[data$Date < as.Date("2020-03-11"), ]
  data_during <- data[data$Date >= as.Date("2020-03-11") & data$Date < as.Date("2021-03-22"), ]
  data_after <- data[data$Date >= as.Date("2021-03-22"), ]
  
  # Categorize distance by kanton and others
  categorize_kanton <- function(df, kanton) {
    df$Category <- factor(ifelse(df$Canton == kanton, kanton, "Other"), levels = c("Other", kanton))
    return(df)
  }

  data_before <- categorize_kanton(data_before, kanton)
  data_during <- categorize_kanton(data_during, kanton)
  data_after <- categorize_kanton(data_after, kanton)
  
  # Plotting function for boxplots
  plot_distance <- function(df, title) {
    ggplot(df, aes(x = Category, y = Distance, fill = Category)) +
      stat_boxplot() +
      scale_fill_manual(values = setNames(c("#88CCEE", "#CC6677"), c("Other", kanton))) +
      labs(x = "Canton", y = "Distance [km]", title = title) +
      theme_minimal() +
      theme(legend.position = "none",
            plot.title = element_text(size = 11, face = "italic", hjust = 0.5),
            axis.title.x = element_text(size = 8), 
            axis.title.y = element_text(size = 8)
      )
  }
  
    # Create plots for each period
  title_before <- "Before Pandemic"
  title_during <- "During Pandemic"
  title_after <- "After Pandemic"
  
  # Create boxplots for each period
  plot_before <- plot_distance(data_before, title_before)
  plot_during <- plot_distance(data_during, title_during)
  plot_after <- plot_distance(data_after, title_after)
  
  # Combine the plots side by side
  combined_plot <- grid.arrange(plot_before, plot_during, plot_after, ncol = 3,
                                         top = textGrob(paste(city_name, "Cantonal Distance Distribution"), 
                                                        gp = gpar(fontsize = 16)))
  
  return(combined_plot)
}

# Test with sample data frames and kanton. 
zurich_plot <- plotDistanceByCanton(Zurich_joined, "ZH", "Zurich")
bellinzona_plot <- plotDistanceByCanton(Bellinzona_joined, "TI", "Bellinzona")  
geneva_plot <- plotDistanceByCanton(Geneva_joined, "GE", "Geneva")

```
```{r}
plotDistance <- function(data, city_name) {
  # Filter data for distance less than or equal to 60
  data <- data[data$Distance <= 60, ]
  
  # Separate data into three periods
  data_before <- data[data$Date < as.Date("2020-03-11"), ]
  data_during <- data[data$Date >= as.Date("2020-03-11") & data$Date < as.Date("2021-03-22"), ]
  data_after <- data[data$Date >= as.Date("2021-03-22"), ]

  # Add a dummy x-axis variable for boxplot
  data_before$x <- 1
  data_during$x <- 1
  data_after$x <- 1

  # Plotting function for boxplots
  plot_distance <- function(df, title_color, title) {
    ggplot(df, aes(x = x, y = Distance)) +
      geom_boxplot(fill = title_color) +
      labs(y = "Distance [km]", title = title) +
      theme_minimal() +
      theme(legend.position = "none",
            plot.title = element_text(size = 11, face = "italic", hjust = 0.5),
            axis.title.x = element_blank(), 
            axis.title.y = element_text(size = 8),
            axis.text.x = element_blank(),
            axis.ticks.x = element_blank()
      )
  }

  # Create plots for each period
  title_before <- "Before Pandemic"
  title_during <- "During Pandemic"
  title_after <- "After Pandemic"
  
  # Create boxplots for each period
  plot_before <- plot_distance(data_before, "#88CCEE", title_before)
  plot_during <- plot_distance(data_during, "#CC6677", title_during)
  plot_after <- plot_distance(data_after, "#117733", title_after)
  
  # Combine the plots side by side
  combined_plot <- grid.arrange(plot_before, plot_during, plot_after, ncol = 3,
                                         top = textGrob(paste(city_name, "Distance Distribution"), 
                                                        gp = gpar(fontsize = 16)))
  
  return(combined_plot)
}

# Test with sample data frames and kanton. 
plotDistance(Zurich_joined, "Zurich")
plotDistance(Bellinzona_joined, "Bellinzona")  
plotDistance(Geneva_joined, "Geneva")

```

### Statistical Distance Analysis

#### Distance Kolmogorov-Smirnov-Test

```{r echo=FALSE, message=FALSE, warning=FALSE}
calculateDistancesByPeriod <- function(data) {
  data_before <- data[data$Date < as.Date("2020-03-11"), ]
  data_during <- data[data$Date >= as.Date("2020-03-11") & data$Date < as.Date("2021-03-22"), ]
  data_after <- data[data$Date >= as.Date("2021-03-22"), ]
  
  # Extract distances from the Distance column
  distances_before <- data_before$Distance
  distances_during <- data_during$Distance
  distances_after <- data_after$Distance
  
  return(list(before = distances_before, during = distances_during, after = distances_after))
}

performKSTestsAndAnalyzeChanges <- function(city_name, data) {
  # Calculate distances for each period
  distances <- calculateDistancesByPeriod(data)

  print(paste("The results for the KS test for", city_name, "are:"))

  # Perform the KS tests between the different periods
  comparisons <- list(
    "Before vs During" = ks.test(distances$before, distances$during),
    "During vs After" = ks.test(distances$during, distances$after)
  )

  # Print the KS test results
  lapply(names(comparisons), function(comp_name) {
    cat(comp_name, "\n")
    print(comparisons[[comp_name]])
  })

  cat("\nThe direction of change in mean distances for", city_name, "are:\n")
  
  # Calculate mean distances for each period
  mean_before <- mean(distances$before, na.rm = TRUE)
  mean_during <- mean(distances$during, na.rm = TRUE)
  mean_after <- mean(distances$after, na.rm = TRUE)
  
  cat("Before: ", mean_before, "\n")
  cat("During: ", mean_during, "\n")
  cat("After: ", mean_after, "\n\n")

  # Analyze the direction of change
  analyzeChange <- function(prev_period, next_period) {
    if (next_period > prev_period) return("Increase")
    else if (next_period < prev_period) return("Decrease")
    else return("No Change")
  }
  
  cat("Change Before to During: ", analyzeChange(mean_before, mean_during), "\n")
  cat("Change During to After: ", analyzeChange(mean_during, mean_after), "\n")
}

# Sample usage with sample data frames and city names.
performKSTestsAndAnalyzeChanges("Zurich", Zurich_joined)
performKSTestsAndAnalyzeChanges("Geneva", Geneva_joined)
performKSTestsAndAnalyzeChanges("Bellinzona", Bellinzona_joined)



```

#### Distance K- Test by Canton

```{r echo=FALSE, message=FALSE, warning=FALSE}
calculateDistancesByPeriod <- function(data) {
  data_before <- data[data$Date < as.Date("2020-03-11"), ]
  data_during <- data[data$Date >= as.Date("2020-03-11") & data$Date < as.Date("2021-03-22"), ]
  data_after <- data[data$Date >= as.Date("2021-03-22"), ]
  
  # Extract distances from the Distance column
  distances_before <- data_before$Distance
  distances_during <- data_during$Distance
  distances_after <- data_after$Distance
  
  return(list(before = distances_before, during = distances_during, after = distances_after))
}

calculateMinDistancesByCanton <- function(data, kanton) {
  # Filter data by kanton and other
  data_kanton <- data[data$Canton == kanton, ]
  data_other <- data[data$Canton != kanton, ]
  
  # Utilize existing calculateMinDistances function
  distances_kanton <- calculateDistancesByPeriod(data_kanton)
  distances_other <- calculateDistancesByPeriod(data_other)
  
  return(list(kanton = distances_kanton, other = distances_other))
}

distances_ZH <- calculateMinDistancesByCanton(Zurich_joined, "ZH")
distances_GE <- calculateMinDistancesByCanton(Geneva_joined, "GE")
distances_TI <- calculateMinDistancesByCanton(Bellinzona_joined, "TI")


performKSTestsAndAnalyzeChanges <- function(city_name, data) {

  print(paste("The results for the KS test for", city_name, "are:"))

  # Perform the KS tests between the different periods
  comparisons <- list(
    "Before vs During" = ks.test(data$before, data$during),
    "During vs After" = ks.test(data$during, data$after)
  )

  # Print the KS test results
  lapply(names(comparisons), function(comp_name) {
    cat(comp_name, "\n")
    print(comparisons[[comp_name]])
  })

  cat("\nThe direction of change in mean distances for", city_name, "are:\n")
  
  # Calculate mean distances for each period
  mean_before <- mean(data$before, na.rm = TRUE)
  mean_during <- mean(data$during, na.rm = TRUE)
  mean_after <- mean(data$after, na.rm = TRUE)
  
  cat("Before: ", mean_before, "\n")
  cat("During: ", mean_during, "\n")
  cat("After: ", mean_after, "\n\n")

  # Analyze the direction of change
  analyzeChange <- function(prev_period, next_period) {
    if (next_period > prev_period) return("Increase")
    else if (next_period < prev_period) return("Decrease")
    else return("No Change")
  }
  
  cat("Change Before to During: ", analyzeChange(mean_before, mean_during), "\n")
  cat("Change During to After: ", analyzeChange(mean_during, mean_after), "\n")
}

cat("Analysis for", "ZH", "in", "Zurich", "\n")
performKSTestsAndAnalyzeChanges(paste("Zurich", "ZH"), distances_ZH$kanton)
cat("Analysis for", "Other", "in", "Zurich", "\n")
performKSTestsAndAnalyzeChanges(paste("Zurich", "ZH"), distances_ZH$other)

cat("Analysis for", "GE", "in", "Geneva", "\n")
performKSTestsAndAnalyzeChanges(paste("Geneva", "ZH"), distances_GE$kanton)
cat("Analysis for", "Other", "in", "Geneva", "\n")
performKSTestsAndAnalyzeChanges(paste("Geneva", "ZH"), distances_GE$other)

cat("Analysis for", "TI", "in", "Bellinzona", "\n")
performKSTestsAndAnalyzeChanges(paste("Bellinzona", "ZH"), distances_TI$kanton)
cat("Analysis for", "Other", "in", "Bellinzona", "\n")
performKSTestsAndAnalyzeChanges(paste("Bellinzona", "ZH"), distances_TI$other)



```
##### Mean Travel Distances by Period

```{r}
calculate_distance_metrics <- function(data_zurich, data_geneva, data_bellinzona) {
  # Helper function to calculate mean distance
  calculate_mean_distance <- function(period_data) {
    mean(period_data$Distance, na.rm = TRUE)
  }

  # Helper function to calculate percentage change
  calculate_percentage_change <- function(rate1, rate2) {
    ((rate2 - rate1) / rate1) * 100
  }

  # Helper function to process each city's data
  process_city_data <- function(city_data) {
    before <- city_data[city_data$Date < as.Date("2020-03-11"), ]
    during <- city_data[city_data$Date >= as.Date("2020-03-11") & city_data$Date < as.Date("2021-03-22"), ]
    after <- city_data[city_data$Date >= as.Date("2021-03-22"), ]

    mean_before <- calculate_mean_distance(before)
    mean_during <- calculate_mean_distance(during)
    mean_after <- calculate_mean_distance(after)

    percentage_change_before_during <- calculate_percentage_change(mean_before, mean_during)
    percentage_change_during_after <- calculate_percentage_change(mean_during, mean_after)
    percentage_change_before_after <- calculate_percentage_change(mean_before, mean_after)

    list(
      MeanDistance = list(Before = mean_before, During = mean_during, After = mean_after),
      PercentageChangeDistance = list(
        Before_During = percentage_change_before_during,
        During_After = percentage_change_during_after,
        Before_After = percentage_change_before_after
      )
    )
  }

  # Process each city's data
  list(
    Zurich = process_city_data(data_zurich),
    Geneva = process_city_data(data_geneva),
    Bellinzona = process_city_data(data_bellinzona)
  )
}

# Usage example:
result <- calculate_distance_metrics(Zurich_Distance, Geneva_Distance, Bellinzona_Distance)
print(result)
```

## Spatial distribution

```{r message=FALSE, warning=FALSE, include=FALSE}

createBoundingBox <- function(coords) {
  buffer <- st_buffer(st_sfc(st_point(coords), crs = 2056), dist = 60000)
  return(st_bbox(buffer))
}

zurich_coords <- c(2684474.6, 1247415.3)
bellinzona_coords <- c(2722573.5, 1115952.8)
geneva_coords <- c(2500343.9, 1116296.7)

zurich_sf <- st_sf(geometry = st_sfc(st_point(zurich_coords), crs = 2056))
bellinzona_sf <- st_sf(geometry = st_sfc(st_point(bellinzona_coords), crs = 2056))
geneva_sf <- st_sf(geometry = st_sfc(st_point(geneva_coords), crs = 2056))

zurich_box <- createBoundingBox(zurich_coords)
bellinzona_box <- createBoundingBox(bellinzona_coords)
geneva_box <- createBoundingBox(geneva_coords)
#geneva_box <- c(xmin = 2481228.7, ymin = 1107287.4, xmax = 2481228.7 + 80000, ymax = 1107287.4 + 80000)

```

### Visitation Mapping

The maps show the admission rates for the three cities of Zurich, Bellinzona, and Geneva for the three respective periods. The admission rate is the percentage of children admitted as a proportion of the total number of children in a postcode. The classifications are quantiles where each of the five classes covers 20% of the complete data set.

#### Visitations Zurich (ZH)

```{r echo=FALSE, message=FALSE, warning=FALSE}

# Function to compute normalized counts, rejoin geometry, and plot
compute_and_plot <- function(city_df, city_name, city_coords) {
  
  # Split data into three time periods
  data_before <- city_df[city_df$Date < as.Date("2020-03-11"), ]
  data_during <- city_df[city_df$Date >= as.Date("2020-03-11") & city_df$Date < as.Date("2021-03-22"), ]
  data_after <- city_df[city_df$Date >= as.Date("2021-03-22"), ]
  
  # Function to prepare and compute normalized counts
  prepare_data <- function(data) {
    # Count the actual number of children per PLZ
    data <- data %>%
      group_by(Zipcode) %>%
      summarise(n = n()) %>%
      ungroup()

    # Compute normalized counts
    data <- data %>% 
      left_join(zipcode_borders %>% 
                st_drop_geometry() %>% 
                dplyr::select(PLZ, Sum), by = c("Zipcode" = "PLZ")) %>% 
      drop_na() %>% 
      filter(Sum != 0) %>%
      mutate(NormalizedCount = (n / Sum) * 100)  # Changed to count per 100 children for normalization
    
    return(data)
  }
  
  data_before <- prepare_data(data_before)
  data_during <- prepare_data(data_during)
  data_after <- prepare_data(data_after)
  
  # Calculate max limit for this specific city across all periods
  max_limit <- max(
    max(data_before$NormalizedCount, na.rm = TRUE), 
    max(data_during$NormalizedCount, na.rm = TRUE), 
    max(data_after$NormalizedCount, na.rm = TRUE)
  )

  plot_for_period <- function(data, period_name) {
    # Rejoin geometry
    city_sf <- left_join(data, zipcode_borders, by = c("Zipcode" = "PLZ")) %>% 
      st_as_sf() %>% 
      st_set_geometry(., "geometry") 

    # Plot on a map
    tm <- tm_shape(st_crop(city_sf,zurich_box)) +
      tm_fill(col = "NormalizedCount", style = "quantile", palette = c("#fee5d9", "#fcae91", "#fb6a4a", "#de2d26", "#a50f15"),
              title = paste0(city_name," - Visitation rates [%]"), legend.reverse = TRUE, n = 5) +
      tm_borders(col = "#cccccc", lwd = 0.1) +
      tm_shape(st_crop(zipcode_borders, zurich_box)) +
      tm_borders(col = "#cccccc", lwd = 0.1) +
      tm_shape(st_crop(canton_borders, zurich_box)) +
      tm_borders(col = "black") +
      tm_shape(city_coords) +
      tm_symbols(shape = 4, size = 0.3, col = "black") +
      tm_shape(st_crop(lakes, zurich_box)) +
      tm_fill(col = "#88CCEE") +
      tm_borders(col = "#cccccc", lwd = 0.1) +
      tm_layout(title = paste0(period_name),
                frame = TRUE,
                inner.margins = c(0.125,0.125,0.125,0.125),
                legend.text.size = 0.6,
                legend.title.size = 0.6,
                legend.position = c("left","top"),
                title.size = 0.9) +
      tm_scale_bar(position = c("right", "bottom"), text.size = 0.5, 
                   lwd = 0.1, color.dark = "grey2", width = 0.15)
            
    # Print the map
    print(tm)
  }

  # Execute for each period
  plot_for_period(data_before, "Visitation Rates Before Pandemic")
  plot_for_period(data_during, "Visitation Rates During Pandemic")
  plot_for_period(data_after, "Visitation Rates After Pandemic")

}

# Execute for each city
compute_and_plot(Zurich_joined, "Zurich", zurich_sf)

```

#### Visitations Geneva (GE)

```{r echo=FALSE, message=FALSE, warning=FALSE}

# Function to compute normalized counts, rejoin geometry, and plot
compute_and_plot <- function(city_df, city_name, city_coords) {
  
  # Split data into three time periods
  data_before <- city_df[city_df$Date < as.Date("2020-03-11"), ]
  data_during <- city_df[city_df$Date >= as.Date("2020-03-11") & city_df$Date < as.Date("2021-03-22"), ]
  data_after <- city_df[city_df$Date >= as.Date("2021-03-22"), ]
  
  # Function to prepare and compute normalized counts
  prepare_data <- function(data) {
    # Count the actual number of children per PLZ
    data <- data %>%
      group_by(Zipcode) %>%
      summarise(n = n()) %>%
      ungroup()

    # Compute normalized counts
    data <- data %>% 
      left_join(zipcode_borders %>% 
                st_drop_geometry() %>% 
                dplyr::select(PLZ, Sum), by = c("Zipcode" = "PLZ")) %>% 
      drop_na() %>% 
      filter(Sum != 0) %>%
      mutate(NormalizedCount = (n / Sum) * 100)  # Changed to count per 100 children for normalization
    
    return(data)
  }
  
  data_before <- prepare_data(data_before)
  data_during <- prepare_data(data_during)
  data_after <- prepare_data(data_after)
  
  # Calculate max limit for this specific city across all periods
  max_limit <- max(
    max(data_before$NormalizedCount, na.rm = TRUE), 
    max(data_during$NormalizedCount, na.rm = TRUE), 
    max(data_after$NormalizedCount, na.rm = TRUE)
  )

  plot_for_period <- function(data, period_name) {
    # Rejoin geometry
    city_sf <- left_join(data, zipcode_borders, by = c("Zipcode" = "PLZ")) %>% 
      st_as_sf() %>% 
      st_set_geometry(., "geometry") 

    # Plot on a map
    tm <- tm_shape(st_crop(city_sf,geneva_box)) +
      tm_fill(col = "NormalizedCount", style = "quantile", palette = c("#fee5d9", "#fcae91", "#fb6a4a", "#de2d26", "#a50f15"),
              title = paste0(city_name," - Visitation rates [%]"), legend.reverse = TRUE, n = 5) +
      tm_borders(col = "#cccccc", lwd = 0.1) +
      tm_shape(st_crop(zipcode_borders, geneva_box)) +
      tm_borders(col = "#cccccc", lwd = 0.1) +
      tm_shape(st_crop(canton_borders, geneva_box)) +
      tm_borders(col = "black") +
      tm_shape(city_coords) +
      tm_symbols(shape = 4, size = 0.3, col = "black") +
      tm_shape(st_crop(lakes, geneva_box)) +
      tm_fill(col = "#88CCEE") +
      tm_borders(col = "#cccccc", lwd = 0.1) +
      tm_layout(title = paste0(period_name),
                frame = TRUE,
                legend.text.size = 0.6,
                legend.title.size = 0.6,
                legend.position = c("left","top"),
                inner.margins = c(0.125,0.125,0.125,0.125),
                title.size = 0.9) +
      tm_scale_bar(position = c("right", "bottom"), text.size = 0.5, lwd = 0.1, color.dark = "grey2", width = 0.15)
      
    # Print the map
    print(tm)
  }

  # Execute for each period
  plot_for_period(data_before, "Visitation Rates Before Pandemic")
  plot_for_period(data_during, "Visitation Rates During Pandemic")
  plot_for_period(data_after, "Visitation Rates After Pandemic")

}

# Execute for each city
compute_and_plot(Geneva_joined, "Geneva",geneva_sf)

```

#### Visitations Ticino (TI)

```{r echo=FALSE, message=FALSE, warning=FALSE}

# Function to compute normalized counts, rejoin geometry, and plot
compute_and_plot <- function(city_df, city_name, city_coords) {
  
  # Split data into three time periods
  data_before <- city_df[city_df$Date < as.Date("2020-03-11"), ]
  data_during <- city_df[city_df$Date >= as.Date("2020-03-11") & city_df$Date < as.Date("2021-03-22"), ]
  data_after <- city_df[city_df$Date >= as.Date("2021-03-22"), ]
  
  # Function to prepare and compute normalized counts
  prepare_data <- function(data) {
    # Count the actual number of children per PLZ
    data <- data %>%
      group_by(Zipcode) %>%
      summarise(n = n()) %>%
      ungroup()

    # Compute normalized counts
    data <- data %>% 
      left_join(zipcode_borders %>% 
                st_drop_geometry() %>% 
                dplyr::select(PLZ, Sum), by = c("Zipcode" = "PLZ")) %>% 
      drop_na() %>% 
      filter(Sum != 0) %>%
      mutate(NormalizedCount = (n / Sum) * 100)  # Changed to count per 100 children for normalization
    
    return(data)
  }
  
  data_before <- prepare_data(data_before)
  data_during <- prepare_data(data_during)
  data_after <- prepare_data(data_after)
  
  # Calculate max limit for this specific city across all periods
  max_limit <- max(
    max(data_before$NormalizedCount, na.rm = TRUE), 
    max(data_during$NormalizedCount, na.rm = TRUE), 
    max(data_after$NormalizedCount, na.rm = TRUE)
  )

  plot_for_period <- function(data, period_name) {
    # Rejoin geometry
    city_sf <- left_join(data, zipcode_borders, by = c("Zipcode" = "PLZ")) %>% 
      st_as_sf(crs = 2056) %>% 
      st_set_geometry(., "geometry")
    
    city_sf <- city_sf %>% st_crop(bellinzona_box)
    
    # Plot on a map
    tm <- tm_shape(city_sf) +
      tm_fill(col = "NormalizedCount", style = "quantile", palette = c("#fee5d9", "#fcae91", "#fb6a4a", "#de2d26", "#a50f15"),
              title = paste0(city_name," - Visitation rates [%]"), legend.reverse = TRUE, n = 5) +
      tm_borders(col = "#cccccc", lwd = 0.1) +
      tm_shape(st_crop(zipcode_borders, bellinzona_box)) +
      tm_borders(col = "#cccccc", lwd = 0.1) +
      tm_shape(st_crop(canton_borders, bellinzona_box)) +
      tm_borders(col = "black") +
      tm_shape(city_coords) +
      tm_symbols(shape = 4, size = 0.3, col = "black") +      
      tm_shape(st_crop(lakes, bellinzona_box)) +
      tm_fill(col = "#88CCEE") +
      tm_borders(col = "#cccccc", lwd = 0.1) +
      tm_layout(title = paste0(period_name),
                frame = TRUE,
                legend.text.size = 0.6,
                legend.title.size = 0.6,
                legend.position = c(0.75,0.1),
                inner.margins = c(0.2,0.2,0.2,0.2),
                title.size = 0.9) +
      tm_scale_bar(position = c("right", "bottom"), text.size = 0.5, lwd = 0.1, color.dark = "grey2", width = 0.15)
      
    # Print the map
    print(tm)
  }

  # Execute for each period
  plot_for_period(data_before, "Visitation Rates Before Pandemic")
  plot_for_period(data_during, "Visitation Rates During Pandemic")
  plot_for_period(data_after, "Visitation Rates After Pandemic")

}

# Execute for each city
compute_and_plot(Bellinzona_joined, "Bellinzona", bellinzona_sf)

```
### Difference in Visitations Mapping (60km Distances)

The following maps show the changes in the allocations for the three cities of Geneva, Bellinzona, and Zurich within 60km to each respective city. The percentage change in admission rates is compared with the period before the pandemic. Again, the five classes are quantiles, covering 20% of the value range.

#### Difference Visitations Zurich (ZH)

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Function to compute normalized counts
calculate_normalized_counts <- function(data) {
  data <- data %>%
    group_by(Zipcode) %>%
    summarise(n = n()) %>%
    ungroup() %>%
    right_join(zipcode_borders %>% 
                 st_drop_geometry() %>% 
                 dplyr::select(PLZ, Sum), by = c("Zipcode" = "PLZ")) %>%
    replace_na(list(n = 0, Sum = 0)) %>%  # Added replacing NA with 0 for Sum
    mutate(NormalizedCount = if_else(Sum == 0, 0, (n / Sum) * 100))  # handling division by zero
  
  print(paste("Normalized counts - Min:", min(data$NormalizedCount), "Max:", max(data$NormalizedCount)))
  return(data)
}

# Function to calculate percentage changes
percentage_changes <- function(before, during, after) {
  data <- before %>%
    dplyr::select(-n, -NormalizedCount) %>%
    mutate(PercentageChangeDuring = (during$NormalizedCount - before$NormalizedCount),
           PercentageChangeAfter = (after$NormalizedCount - before$NormalizedCount))
  
  print(paste("Percentage changes during - Min:", min(data$PercentageChangeDuring), "Max:", max(data$PercentageChangeDuring)))
  print(paste("Percentage changes after - Min:", min(data$PercentageChangeAfter), "Max:", max(data$PercentageChangeAfter)))
  return(data)
}

# Make sure to have the necessary data and libraries loaded before running the function

# Apply the functions
compute <- function(city_df, city_name) {
  
  city_df <- city_df[city_df$Distance <= 60, ]
  # Split the data into three periods
  data_before <- city_df[city_df$Date < as.Date("2020-03-11"), ]
  data_during <- city_df[city_df$Date >= as.Date("2020-03-11") & city_df$Date < as.Date("2021-03-22"), ]
  data_after <- city_df[city_df$Date >= as.Date("2021-03-22"), ]

  before <- calculate_normalized_counts(data_before)
  during <- calculate_normalized_counts(data_during)
  after <- calculate_normalized_counts(data_after)

  changes <- percentage_changes(before, during, after)
    
  changes <- changes %>%
    filter(PercentageChangeDuring != 0 | PercentageChangeAfter != 0)
}

# Execute for each city
computed_Zurich_df <- compute(Zurich_joined, "Zurich")

plot_maps <- function(data, city_name, bbox, city_coords) {
  plot_for_period <- function(data, change_column, title) {
    city_sf <- left_join(data, zipcode_borders, by = c("Zipcode" = "PLZ")) %>%
      st_as_sf() %>% 
      st_set_geometry(., "geometry") %>%
      st_crop(., bbox)

    labels = c("Very Negative", "Negative", "Neutral", "Positive", "Very Positive")
  
    # Create the tmap plot
    tm <- tm_shape(city_sf) +
          tm_fill(col = change_column, style = "quantile", 
                  palette= c( "#A6611A","#DFC27D","#F5F5F5","#80CDC1","#018571"),
                  title = paste0(city_name," - Change In Visitation Rates [%]"), legend.reverse = TRUE) +
          tm_borders(col = "#cccccc", lwd = 0.1) +
          tm_shape(st_crop(zipcode_borders, bbox)) +
          tm_borders(col = "#cccccc", lwd = 0.1) +
          tm_shape(st_crop(canton_borders, bbox)) +
          tm_borders(col = "black") +
          tm_shape(city_coords) +
          tm_symbols(shape = 4, size = 0.3, col = "black") +
          tm_shape(st_crop(lakes, bbox)) +
          tm_fill(col = "#88CCEE") +
          tm_borders(col = "#cccccc", lwd = 0.1) +
          tm_layout(title = paste0(title),
                    frame = TRUE,
                    legend.position = c("left", "top"),
                    legend.text.size = 0.6,
                    legend.title.size = 0.6,
                    inner.margins = c(0.125,0.125,0.3,0.18),
                    title.size = 0.9,
                    main.title.fontface = "italic", 
                    main.title.fontfamily = "sans") +
          tm_scale_bar(position = c("right", "bottom"), text.size = 0.5, 
                       bg.color = "white", bg.alpha = 1)
    
    # Print the map
    print(tm)
  }

  plot_for_period(data, "PercentageChangeDuring", "Change in Visitation Rates Before to During Pandemic")
  plot_for_period(data, "PercentageChangeAfter", "Change in Visitation Rates Before to After Pandemic")
}

plot_maps(computed_Zurich_df, "Zurich", zurich_box, zurich_sf)

plot_maps <- function(data, city_name, bbox, city_coords) {
  plot_for_period <- function(data, change_column, title) {
    # Join the data with the spatial data
    city_sf <- left_join(data, zipcode_borders, by = c("Zipcode" = "PLZ")) %>%
      st_as_sf() %>% 
      st_set_geometry(., "geometry") %>%
      st_crop(., bbox)

    # Calculate the breaks for the quantiles
    quantiles <- quantile(data[[change_column]], probs = c(0.2, 0.8), na.rm = TRUE)

    # Define breaks for the highest and lowest 20%
    breaks <- c(-Inf, quantiles[1], quantiles[2], Inf)

    # Create custom labels
    labels <- c(
      sprintf("%0.2f to %0.2f (Lowest 20%%)", min(data[[change_column]], na.rm = TRUE), quantiles[1]),
      sprintf("%0.2f to %0.2f (Middle 60%%)", quantiles[1], quantiles[2]),
      sprintf("%0.2f to %0.2f (Highest 20%%)", quantiles[2], max(data[[change_column]], na.rm = TRUE))
    )

    # Define a palette with three colors, one for each class
    palette <- c("#A6611A", "#F5F5F5", "#018571")  # Middle color should be neutral

    # Create the tmap plot with fixed breaks and custom labels
    tm <- tm_shape(city_sf) +
          tm_fill(col = change_column, style = "fixed", breaks = breaks,
                  palette = palette,
                  labels = labels,
                  title = paste0(city_name," - Change In Visitation Rates [%]"),
                  legend.reverse = TRUE) +
          tm_borders(col = "#cccccc", lwd = 0.1) +
          tm_shape(st_crop(zipcode_borders, bbox)) +
          tm_borders(col = "#cccccc", lwd = 0.1) +
          tm_shape(st_crop(canton_borders, bbox)) +
          tm_borders(col = "black") +
          tm_shape(city_coords) +
          tm_symbols(shape = 4, size = 0.3, col = "black") +
          tm_shape(st_crop(lakes, bbox)) +
          tm_fill(col = "#88CCEE") +
          tm_borders(col = "#cccccc", lwd = 0.1) +
          tm_layout(title = paste0(title),
                    frame = TRUE,
                    legend.position = c("left", "top"),
                    legend.text.size = 0.6,
                    legend.title.size = 0.6,
                    inner.margins = c(0.125,0.125,0.3,0.18),
                    title.size = 0.9,
                    main.title.fontface = "italic", 
                    main.title.fontfamily = "sans") +
          tm_scale_bar(position = c("right", "bottom"), text.size = 0.5, 
                       bg.color = "white", bg.alpha = 1)
    
    # Print the map
    print(tm)
  }

  plot_for_period(data, "PercentageChangeDuring", "Highest and Lowest Change in Visitation Rates Before to During Pandemic")
  plot_for_period(data, "PercentageChangeAfter", "Highest and Lowest Change in Visitation Rates Before to After Pandemic")
}

plot_maps(computed_Zurich_df, "Zurich", zurich_box, zurich_sf)


```

```{r}
# Function to get top and bottom 5 zip codes for each period
get_top_bottom_zipcodes <- function(data, value_column) {
  top_5 <- data %>%
    arrange(desc(!!sym(value_column))) %>%
    slice_head(n = 5)

  bottom_5 <- data %>%
    arrange(!!sym(value_column)) %>%
    slice_head(n = 5)

  list(Top = top_5, Bottom = bottom_5)
}

# Applying the function to the computed_Zurich_df
# Assuming computed_Zurich_df is already computed and available

# For the period "during"
top_bottom_during <- get_top_bottom_zipcodes(computed_Zurich_df, "PercentageChangeDuring")

# For the period "after"
top_bottom_after <- get_top_bottom_zipcodes(computed_Zurich_df, "PercentageChangeAfter")

# Displaying results
print("Top and bottom 5 zip codes for 'during' period:")
print(top_bottom_during)
print("Top and bottom 5 zip codes for 'after' period:")
print(top_bottom_after)

```


#### Difference Visitations Geneva (GE)

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Function to compute normalized counts
calculate_normalized_counts <- function(data) {
  data <- data %>%
    group_by(Zipcode) %>%
    summarise(n = n()) %>%
    ungroup() %>%
    right_join(zipcode_borders %>% 
                 st_drop_geometry() %>% 
                 dplyr::select(PLZ, Sum), by = c("Zipcode" = "PLZ")) %>%
    replace_na(list(n = 0, Sum = 0)) %>%  # Added replacing NA with 0 for Sum
    mutate(NormalizedCount = if_else(Sum == 0, 0, (n / Sum) * 100))  # handling division by zero
  return(data)
}

# Function to calculate percentage changes
percentage_changes <- function(before, during, after) {
  data <- before %>%
    dplyr::select(-n, -NormalizedCount) %>%
    mutate(PercentageChangeDuring = (during$NormalizedCount - before$NormalizedCount),
           PercentageChangeAfter = (after$NormalizedCount - before$NormalizedCount)) 
  
  return(data)
}

# Apply the functions
compute <- function(city_df, city_name) {
  city_df <- city_df[city_df$Distance <= 60, ]
  # Split the data into three periods
  data_before <- city_df[city_df$Date < as.Date("2020-03-11"), ]
  data_during <- city_df[city_df$Date >= as.Date("2020-03-11") & city_df$Date < as.Date("2021-03-22"), ]
  data_after <- city_df[city_df$Date >= as.Date("2021-03-22"), ]

  before <- calculate_normalized_counts(data_before)
  during <- calculate_normalized_counts(data_during)
  after <- calculate_normalized_counts(data_after)

  changes <- percentage_changes(before, during, after)
  changes <- changes %>%
    filter(PercentageChangeDuring != 0 | PercentageChangeAfter != 0)
}

# Execute for each city
computed_Geneva_df <- compute(Geneva_joined, "Geneva")

plot_maps <- function(data, city_name, bbox, city_coords) {
  plot_for_period <- function(data, change_column, title) {
    city_sf <- left_join(data, zipcode_borders, by = c("Zipcode" = "PLZ")) %>%
      st_as_sf() %>% 
      st_set_geometry(., "geometry") %>%
      st_crop(., bbox)

    # Create the tmap plot
    tm <- tm_shape(city_sf) +
      tm_fill(col = change_column, style = "quantile", 
                  palette= c( "#A6611A","#DFC27D","#F5F5F5","#80CDC1","#018571"),
                  title = paste0(city_name," - Change In Visitation Rates [%]"), legend.reverse = TRUE) +
          tm_borders(col = "#cccccc", lwd = 0.1) +
          tm_shape(st_crop(zipcode_borders, bbox)) +
          tm_borders(col = "#cccccc", lwd = 0.1) +
          tm_shape(st_crop(canton_borders, bbox)) +
          tm_borders(col = "black") +
          tm_shape(city_coords) +
          tm_symbols(shape = 4, size = 0.3, col = "black") +
          tm_shape(st_crop(lakes, bbox)) +
          tm_fill(col = "#88CCEE") +
          tm_borders(col = "#cccccc", lwd = 0.1) +
          tm_layout(title = paste0(title),
                    frame = TRUE,
                    legend.position = c("left", "top"),
                    legend.text.size = 0.6,
                    legend.title.size = 0.6,
                    inner.margins = c(0.1,0.125,0.25,0.2),
                    title.size =0.9,
                    main.title.fontface = "italic", 
                    main.title.fontfamily = "sans") +
          tm_scale_bar(position = c("right", "bottom"), text.size = 0.5, 
                       bg.color = "white", bg.alpha = 1)
    
    # Print the map
    print(tm)
  }

  plot_for_period(data, "PercentageChangeDuring", "Change in Visitation Rates Before to During Pandemic")
  plot_for_period(data, "PercentageChangeAfter", "Change in Visitation Rates Before to After Pandemic")
}

plot_maps(computed_Geneva_df, "Geneva", geneva_box, geneva_sf)

plot_maps <- function(data, city_name, bbox, city_coords) {
  plot_for_period <- function(data, change_column, title) {
    # Join the data with the spatial data
    city_sf <- left_join(data, zipcode_borders, by = c("Zipcode" = "PLZ")) %>%
      st_as_sf() %>% 
      st_set_geometry(., "geometry") %>%
      st_crop(., bbox)

    # Calculate the breaks for the quantiles
    quantiles <- quantile(data[[change_column]], probs = c(0.2, 0.8), na.rm = TRUE)

    # Define breaks for the highest and lowest 20%
    breaks <- c(-Inf, quantiles[1], quantiles[2], Inf)

    # Create custom labels
    labels <- c(
      sprintf("%0.2f to %0.2f (Lowest 20%%)", min(data[[change_column]], na.rm = TRUE), quantiles[1]),
      sprintf("%0.2f to %0.2f (Middle 60%%)", quantiles[1], quantiles[2]),
      sprintf("%0.2f to %0.2f (Highest 20%%)", quantiles[2], max(data[[change_column]], na.rm = TRUE))
    )

    # Define a palette with three colors, one for each class
    palette <- c("#A6611A", "#F5F5F5", "#018571")  # Middle color should be neutral

    # Create the tmap plot with fixed breaks and custom labels
    tm <- tm_shape(city_sf) +
          tm_fill(col = change_column, style = "fixed", breaks = breaks,
                  palette = palette,
                  labels = labels,
                  title = paste0(city_name," - Change In Visitation Rates [%]"),
                  legend.reverse = TRUE) +
          tm_borders(col = "#cccccc", lwd = 0.1) +
          tm_shape(st_crop(zipcode_borders, bbox)) +
          tm_borders(col = "#cccccc", lwd = 0.1) +
          tm_shape(st_crop(canton_borders, bbox)) +
          tm_borders(col = "black") +
          tm_shape(city_coords) +
          tm_symbols(shape = 4, size = 0.3, col = "black") +
          tm_shape(st_crop(lakes, bbox)) +
          tm_fill(col = "#88CCEE") +
          tm_borders(col = "#cccccc", lwd = 0.1) +
          tm_layout(title = paste0(title),
                    frame = TRUE,
                    legend.position = c("left", "top"),
                    legend.text.size = 0.6,
                    legend.title.size = 0.6,
                    inner.margins = c(0.1,0.125,0.25,0.2),
                    title.size = 0.9,
                    main.title.fontface = "italic", 
                    main.title.fontfamily = "sans") +
          tm_scale_bar(position = c("right", "bottom"), text.size = 0.5, 
                       bg.color = "white", bg.alpha = 1)
    
    # Print the map
    print(tm)
  }

  plot_for_period(data, "PercentageChangeDuring", "Highest and Lowest Change in Visitation Rates Before to During Pandemic")
  plot_for_period(data, "PercentageChangeAfter", "Highest and Lowest Change in Visitation Rates Before to After Pandemic")
}

plot_maps(computed_Geneva_df, "Geneva", geneva_box, geneva_sf)

```
```{r}
# Function to get top and bottom 5 zip codes for each period
get_top_bottom_zipcodes <- function(data, value_column) {
  top_5 <- data %>%
    arrange(desc(!!sym(value_column))) %>%
    slice_head(n = 5)

  bottom_5 <- data %>%
    arrange(!!sym(value_column)) %>%
    slice_head(n = 5)

  list(Top = top_5, Bottom = bottom_5)
}

# Applying the function to the computed_Zurich_df
# Assuming computed_Zurich_df is already computed and available

# For the period "during"
top_bottom_during <- get_top_bottom_zipcodes(computed_Geneva_df, "PercentageChangeDuring")

# For the period "after"
top_bottom_after <- get_top_bottom_zipcodes(computed_Geneva_df, "PercentageChangeAfter")

# Displaying results
print("Top and bottom 5 zip codes for 'during' period:")
print(top_bottom_during)
print("Top and bottom 5 zip codes for 'after' period:")
print(top_bottom_after)
```



#### Difference Visitations Ticino (TI)

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Function to compute normalized counts
calculate_normalized_counts <- function(data) {
  data <- data %>%
    group_by(Zipcode) %>%
    summarise(n = n()) %>%
    ungroup() %>%
    right_join(zipcode_borders %>% 
                 st_drop_geometry() %>% 
                 dplyr::select(PLZ, Sum), by = c("Zipcode" = "PLZ")) %>%
    replace_na(list(n = 0, Sum = 0)) %>%  # Added replacing NA with 0 for Sum
    mutate(NormalizedCount = if_else(Sum == 0, 0, (n / Sum) * 100))  # handling division by zero
  return(data)
}

# Function to calculate percentage changes
percentage_changes <- function(before, during, after) {
  data <- before %>%
    dplyr::select(-n, -NormalizedCount) %>%
    mutate(PercentageChangeDuring = (during$NormalizedCount - before$NormalizedCount),
           PercentageChangeAfter = (after$NormalizedCount - before$NormalizedCount))
  return(data)
}

# Make sure to have the necessary data and libraries loaded before running the function

# Apply the functions
compute <- function(city_df, city_name) {
  city_df <- city_df[city_df$Distance <= 60, ]
  # Split the data into three periods
  data_before <- city_df[city_df$Date < as.Date("2020-03-11"), ]
  data_during <- city_df[city_df$Date >= as.Date("2020-03-11") & city_df$Date < as.Date("2021-03-22"), ]
  data_after <- city_df[city_df$Date >= as.Date("2021-03-22"), ]

  before <- calculate_normalized_counts(data_before)
  during <- calculate_normalized_counts(data_during)
  after <- calculate_normalized_counts(data_after)

  changes <- percentage_changes(before, during, after)
  changes <- changes %>%
    filter(PercentageChangeDuring != 0 | PercentageChangeAfter != 0)
}

# Execute for each city
computed_Bellinzona_df <- compute(Bellinzona_joined, "Bellinzona")

plot_maps <- function(data, city_name, bbox, city_coords) {
  plot_for_period <- function(data, change_column, title) {
    city_sf <- left_join(data, zipcode_borders, by = c("Zipcode" = "PLZ")) %>%
      st_as_sf() %>% 
      st_set_geometry(., "geometry") %>%
      st_crop(., bbox)

    # Create the tmap plot
    tm <- tm_shape(city_sf) +
          tm_fill(col = change_column, style = "quantile", n = 5, 
                  palette= c( "#A6611A","#DFC27D","#F5F5F5","#80CDC1","#018571"),
                  title = paste0(city_name," - Change In Visitation Rates [%]")) +
          tm_borders(col = "#cccccc", lwd = 0.1) +
          tm_shape(st_crop(zipcode_borders, bbox)) +
          tm_borders(col = "#cccccc", lwd = 0.1) +
          tm_shape(st_crop(canton_borders, bbox)) +
          tm_borders(col = "black") +
          tm_shape(city_coords) +
          tm_symbols(shape = 4, size = 0.3, col = "black") +
          tm_shape(st_crop(lakes, bbox)) +
          tm_fill(col = "#88CCEE") +
          tm_borders(col = "#cccccc", lwd = 0.1) +
          tm_layout(title = paste0(title),
                    frame = TRUE,
                    legend.text.size = 0.6,
                    legend.title.size = 0.6,
                    inner.margins = c(0.175,0.2,0.25,0.35),
                    title.size = 0.9,
                    main.title.fontface = "italic", 
                    main.title.fontfamily = "sans") +
          tm_scale_bar(position = c("right", "bottom"), text.size = 0.5, 
                       bg.color = "white", bg.alpha = 1)
    
    # Print the map
    print(tm)
  }

  plot_for_period(data, "PercentageChangeDuring", "Change in Visitation Rates Before to During Pandemic")
  plot_for_period(data, "PercentageChangeAfter", "Change in Visitation Rates Before to After Pandemic")
}

plot_maps(computed_Bellinzona_df, "Bellinzona", bellinzona_box, bellinzona_sf)

plot_maps <- function(data, city_name, bbox, city_coords) {
  plot_for_period <- function(data, change_column, title) {
    # Join the data with the spatial data
    city_sf <- left_join(data, zipcode_borders, by = c("Zipcode" = "PLZ")) %>%
      st_as_sf() %>% 
      st_set_geometry(., "geometry") %>%
      st_crop(., bbox)

    # Calculate the breaks for the quantiles
    quantiles <- quantile(data[[change_column]], probs = c(0.2, 0.8), na.rm = TRUE)

    # Define breaks for the highest and lowest 20%
    breaks <- c(-Inf, quantiles[1], quantiles[2], Inf)

    # Create custom labels
    labels <- c(
      sprintf("%0.2f to %0.2f (Lowest 20%%)", min(data[[change_column]], na.rm = TRUE), quantiles[1]),
      sprintf("%0.2f to %0.2f (Middle 60%%)", quantiles[1], quantiles[2]),
      sprintf("%0.2f to %0.2f (Highest 20%%)", quantiles[2], max(data[[change_column]], na.rm = TRUE))
    )

    # Define a palette with three colors, one for each class
    palette <- c("#A6611A", "#F5F5F5", "#018571")  # Middle color should be neutral

    # Create the tmap plot with fixed breaks and custom labels
    tm <- tm_shape(city_sf) +
          tm_fill(col = change_column, style = "fixed", breaks = breaks,
                  palette = palette,
                  labels = labels,
                  title = paste0(city_name," - Change In Visitation Rates [%]"),
                  legend.reverse = TRUE) +
          tm_borders(col = "#cccccc", lwd = 0.1) +
          tm_shape(st_crop(zipcode_borders, bbox)) +
          tm_borders(col = "#cccccc", lwd = 0.1) +
          tm_shape(st_crop(canton_borders, bbox)) +
          tm_borders(col = "black") +
          tm_shape(city_coords) +
          tm_symbols(shape = 4, size = 0.3, col = "black") +
          tm_shape(st_crop(lakes, bbox)) +
          tm_fill(col = "#88CCEE") +
          tm_borders(col = "#cccccc", lwd = 0.1) +
          tm_layout(title = paste0(title),
                    frame = TRUE,
                    legend.text.size = 0.6,
                    legend.title.size = 0.6,
                    inner.margins = c(0.175,0.2,0.25,0.35),
                    title.size = 0.9,
                    main.title.fontface = "italic", 
                    main.title.fontfamily = "sans") +
          tm_scale_bar(position = c("right", "bottom"), text.size = 0.5, 
                       bg.color = "white", bg.alpha = 1)
    
    # Print the map
    print(tm)
  }

  plot_for_period(data, "PercentageChangeDuring", "Highest and Lowest Change in Visitation Rates Before to During Pandemic")
  plot_for_period(data, "PercentageChangeAfter", "Highest and Lowest Change in Visitation Rates Before to After Pandemic")
}


plot_maps(computed_Bellinzona_df, "Bellinzona", bellinzona_box, bellinzona_sf)

```
```{r}
# Function to get top and bottom 5 zip codes for each period
get_top_bottom_zipcodes <- function(data, value_column) {
  top_5 <- data %>%
    arrange(desc(!!sym(value_column))) %>%
    slice_head(n = 5)

  bottom_5 <- data %>%
    arrange(!!sym(value_column)) %>%
    slice_head(n = 5)

  list(Top = top_5, Bottom = bottom_5)
}

# Applying the function to the computed_Zurich_df
# Assuming computed_Zurich_df is already computed and available

# For the period "during"
top_bottom_during <- get_top_bottom_zipcodes(computed_Bellinzona_df, "PercentageChangeDuring")

# For the period "after"
top_bottom_after <- get_top_bottom_zipcodes(computed_Bellinzona_df, "PercentageChangeAfter")

# Displaying results
print("Top and bottom 5 zip codes for 'during' period:")
print(top_bottom_during)
print("Top and bottom 5 zip codes for 'after' period:")
print(top_bottom_after)
```

### Admission Rates

```{r}
# Filter data for each time period for each city
geneva_before <- Geneva[Geneva$Date < as.Date("2020-03-11"), ]
geneva_during <- Geneva[Geneva$Date >= as.Date("2020-03-11") & Geneva$Date < as.Date("2021-03-22"), ]
geneva_after <- Geneva[Geneva$Date >= as.Date("2021-03-22"), ]

bellinzona_before <- Bellinzona[Bellinzona$Date < as.Date("2020-03-11"), ]
bellinzona_during <- Bellinzona[Bellinzona$Date >= as.Date("2020-03-11") & Bellinzona$Date < as.Date("2021-03-22"), ]
bellinzona_after <- Bellinzona[Bellinzona$Date >= as.Date("2021-03-22"), ]

zurich_before <- Zurich[Zurich$Date < as.Date("2020-03-11"), ]
zurich_during <- Zurich[Zurich$Date >= as.Date("2020-03-11") & Zurich$Date < as.Date("2021-03-22"), ]
zurich_after <- Zurich[Zurich$Date >= as.Date("2021-03-22"), ]

# Assuming 'data' contains the 'Sum' column for all children in Switzerland
total_children_switzerland <- 1755213

# Function to calculate hospitalization rate
calculate_hospitalization_rate <- function(period_data) {
  total_hospitalizations <- nrow(period_data)
  return (total_hospitalizations / total_children_switzerland)
}

# Calculate rates for each city and period
rate_before_geneva <- calculate_hospitalization_rate(geneva_before)
rate_during_geneva <- calculate_hospitalization_rate(geneva_during)
rate_after_geneva <- calculate_hospitalization_rate(geneva_after)

rate_before_bellinzona <- calculate_hospitalization_rate(bellinzona_before)
rate_during_bellinzona <- calculate_hospitalization_rate(bellinzona_during)
rate_after_bellinzona <- calculate_hospitalization_rate(bellinzona_after)

rate_before_zurich <- calculate_hospitalization_rate(zurich_before)
rate_during_zurich <- calculate_hospitalization_rate(zurich_during)
rate_after_zurich <- calculate_hospitalization_rate(zurich_after)

# Function to calculate percentage change
calculate_percentage_change <- function(rate1, rate2) {
  return ((rate2 - rate1) / rate1 * 100)
}

# Calculate percentage changes for each city
percentage_change_geneva_before_during <- calculate_percentage_change(rate_before_geneva, rate_during_geneva)
percentage_change_geneva_during_after <- calculate_percentage_change(rate_during_geneva, rate_after_geneva)
percentage_change_geneva_before_after <- calculate_percentage_change(rate_before_geneva, rate_after_geneva)

percentage_change_bellinzona_before_during <- calculate_percentage_change(rate_before_bellinzona, rate_during_bellinzona)
percentage_change_bellinzona_during_after <- calculate_percentage_change(rate_during_bellinzona, rate_after_bellinzona)
percentage_change_bellinzona_before_after <- calculate_percentage_change(rate_before_bellinzona, rate_after_bellinzona)

percentage_change_zurich_before_during <- calculate_percentage_change(rate_before_zurich, rate_during_zurich)
percentage_change_zurich_during_after <- calculate_percentage_change(rate_during_zurich, rate_after_zurich)
percentage_change_zurich_before_after <- calculate_percentage_change(rate_before_zurich, rate_after_zurich)

# Output the results
list(
  Geneva = list(
    Before = rate_before_geneva, 
    During = rate_during_geneva, 
    After = rate_after_geneva, 
    PercentageChange = list(
      Before_During = percentage_change_geneva_before_during,
      During_After = percentage_change_geneva_during_after,
      Before_After = percentage_change_geneva_before_after
    )
  ),
  Bellinzona = list(
    Before = rate_before_bellinzona, 
    During = rate_during_bellinzona, 
    After = rate_after_bellinzona, 
    PercentageChange = list(
      Before_During = percentage_change_bellinzona_before_during,
      During_After = percentage_change_bellinzona_during_after,
      Before_After = percentage_change_bellinzona_before_after
    )
  ),
  Zurich = list(
    Before = rate_before_zurich, 
    During = rate_during_zurich, 
    After = rate_after_zurich, 
    PercentageChange = list(
      Before_During = percentage_change_zurich_before_during,
      During_After = percentage_change_zurich_during_after,
      Before_After = percentage_change_zurich_before_after
    )
  )
)


```

## Relevant factors

### Separate Cities

```{r echo=FALSE, message=FALSE, warning=FALSE}

# Updated function to model the data with 'Period'
poisson_model <- function(data, city_name) {
  data$Visitation <- 1
  # Model the data using Poisson regression including the 'Period' variable
  model <- glm(formula = Visitation ~ factor(TriageCategory) + Age + factor(Gender) + 
                 factor(Reason) + factor(Type) + Sum + Distance + factor(Period), 
     
                         family = "poisson", data = data)
  
  summary(model)
  
  # Print the summary
  cat("\n", city_name, "\n")
  print(summary(model))
  
  return(model)
}

# Function to process each city's data
process_city_data <- function(city_df, city_name) {
  cat("\nProcessing data for", city_name, "\n")

  # Add 'Period' column to the dataset
  city_df$Period <- ifelse(city_df$Date < as.Date("2020-03-11"), 1,
                           ifelse(city_df$Date < as.Date("2021-03-22"), 2, 3))
  # Run Poisson regression model on the entire dataset
  poisson_model(city_df, city_name)
}

# Execute for each city
process_city_data(Zurich_joined, "Zurich")
process_city_data(Geneva_joined, "Geneva")
process_city_data(Bellinzona_joined, "Bellinzona")

```

### Combined Cities

```{r}
# Function to model the data with 'Period' and 'City'
poisson_model <- function(data) {
  data$Visitation <- 1
  # Model the data using Poisson regression including the 'Period' and 'City' variables
  model <- glm(formula = Visitation ~ factor(TriageCategory) + Age + factor(Gender) + 
                 factor(Reason) + factor(Type) + Sum + Distance + factor(Period) + 
                 factor(City), 
               family = "poisson", data = data)
  
  # Print the summary
  print(summary(model))
  
  return(model)
}

# Function to add 'Period' column and 'City' identifier to each city's data
add_city_info <- function(city_df, city_name) {
  city_df$Period <- ifelse(city_df$Date < as.Date("2020-03-11"), 1,
                           ifelse(city_df$Date < as.Date("2021-03-22"), 2, 3))
  city_df$City <- ifelse(city_name == "Zurich", 1,
                         ifelse(city_name == "Bellinzona", 2, 3))
  return(city_df)
}

# Add city info and combine datasets
zurich_processed <- add_city_info(Zurich_joined, "Zurich")
geneva_processed <- add_city_info(Geneva_joined, "Geneva")
bellinzona_processed <- add_city_info(Bellinzona_joined, "Bellinzona")
combined_df <- rbind(zurich_processed, geneva_processed, bellinzona_processed)

# Run Poisson regression model on the combined dataset
combined_model <- poisson_model(combined_df)

```

```{r}
combined_df_level <- combined_df
ref_tables <- list()
for (col in colnames(combined_df_level)) {
  # check if the column is character type for the current iteration of the loop
  if (is.character(combined_df_level[[col]])) {
    # recode to numeric values
    levels <- unique(combined_df_level[[col]])
    combined_df_level[[col]] <- as.numeric(factor(combined_df_level[[col]], levels = levels))
    # create reference table data frame
    ref_accident_data <- data.frame(value = 1:length(levels), label = levels)
    # add reference table data frame to list
    ref_tables[[col]] <- ref_accident_data
  }
}
```

```{r}
# Define a custom aggregation function
custom_aggregate <- function(x) {
  if (is.numeric(x)) {
    return(mean(x))
  } else {
    return(prop.table(table(x)))
  }
}

# Apply custom aggregation
agg_data <- aggregate(cbind(Age, TriageCategory, Sum, Distance, Period, Month, Day, Year, City, Reason, Type, Gender, Nationality,COVID) ~ Zipcode, 
                      data = combined_df_level, FUN = custom_aggregate)

# Poisson model
poisson_model_plz <- glm(Zipcode ~ Age + Sum + Distance + Period + TriageCategory + Month + Day + Year + City + Reason + Type + Gender + Nationality + COVID,data = agg_data, family = "poisson", weights = rep(1, nrow(agg_data)))

# Model summary
summary(poisson_model_plz)

```

```{r}
# Load the lme4 package
library(lme4)

# Define a custom aggregation function
custom_aggregate <- function(x) {
  if (is.numeric(x)) {
    return(mean(x))
  } else {
    return(prop.table(table(x)))
  }
}

# Apply custom aggregation
agg_data <- aggregate(cbind(Age, TriageCategory, Sum, Distance, Period, Month, Day, Year, City, Reason, Type, Gender, Nationality,COVID) ~ Zipcode, 
                      data = combined_df_level, FUN = custom_aggregate)
# List of numeric variables to scale
numeric_vars <- c("Age", "TriageCategory", "Sum", "Distance", "Period", "Month", "Day", "Year", "City", "Reason", "Type", "Gender", "Nationality","COVID")

# Scale numeric variables
agg_data[numeric_vars] <- lapply(agg_data[numeric_vars], scale)

# Generalized linear mixed-effects model (glmer)
glmer_model_plz <- glmer(Zipcode ~ Age + Sum + Distance + Period + TriageCategory + Month + Day + Year + City + Reason + Type + Gender + Nationality + COVID +(1 | Zipcode),  # Random effect for Zipcode
                         data = agg_data, family = poisson(), weights = rep(1, nrow(agg_data)),
                         control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 100000)))

# Model summary
summary(glmer_model_plz)

```

## Excursus: Temporal Analysis

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Modified function to include normalization
plot_weekday_counts <- function(city_df, city_name, normalisation_before, normalisation_during, normalisation_after) {
  
  # Add a new column for the weekday extracted from the Date column
  city_df <- city_df %>%
    mutate(Weekday = weekdays(as.Date(Date, format="%Y-%m-%d")))
  
  # Modified function to prepare data: group by weekday and count occurrences, then normalize
  prepare_data <- function(data, period, normalisation) {
    data %>%
      group_by(Weekday) %>%
      summarise(Count = mean(n())/normalisation) %>%
      ungroup() %>%
      mutate(Period = period, 
             Weekday = factor(Weekday, levels = c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday","Sunday")))
  }

  # Apply the function to each time period with corresponding normalization values
  data_before <- prepare_data(city_df[city_df$Date < as.Date("2020-03-11"), ], "Before Pandemic", normalisation_before)
  data_during <- prepare_data(city_df[city_df$Date >= as.Date("2020-03-11") & city_df$Date < as.Date("2021-03-22"), ], "During Pandemic", normalisation_during)
  data_after <- prepare_data(city_df[city_df$Date >= as.Date("2021-03-22"), ], "After Pandemic", normalisation_after)

  combined_data <- rbind(data_before, data_during, data_after)
  
  # Order the Period factor levels
  combined_data$Period <- factor(combined_data$Period, 
                                 levels = c("Before Pandemic", "During Pandemic", "After Pandemic"))

  # Plot
  ggplot(combined_data, aes(x = Weekday, y = Count, fill = Period)) +
    geom_bar(stat = "identity", position = "dodge") +
    labs(
      title = paste("Visitations per Weekday in", city_name),
      x = "Weekday",
      y = "Normalized Count") +
    theme_minimal() +
      theme(plot.title = element_text(size = 11, face = "italic", hjust = 0.5),
            axis.title.x = element_text(size = 8), 
            axis.title.y = element_text(size = 8),
            legend.position = "bottom"
      )+
    scale_fill_manual(values = c("Before Pandemic" = "#88CCEE", "During Pandemic" = "#CC6677", "After Pandemic" = "#117733"))
}

# Apply the function to each city with normalization factors
normalisation_before <- 24.32
normalisation_during <- 12.35
normalisation_after <- 11.21

plot_weekday_counts(Zurich_joined, "Zurich", normalisation_before, normalisation_during, normalisation_after)
plot_weekday_counts(Bellinzona_joined, "Bellinzona", normalisation_before, normalisation_during, normalisation_after)
plot_weekday_counts(Geneva_joined, "Geneva", normalisation_before, normalisation_during, normalisation_after)


```

## Archive
### Difference in Visitations Mapping (All Distances)

The following maps show the changes in the allocations for the three cities of Geneva, Bellinzona, and Zurich. The percentage change in admission rates is compared with the period before the pandemic. Again, the five classes are quantiles, covering 20% of the value range.

#### Difference Visitations Zurich (ZH)

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Function to compute normalized counts
calculate_normalized_counts <- function(data) {
  data <- data %>%
    group_by(Zipcode) %>%
    summarise(n = n()) %>%
    ungroup() %>%
    right_join(zipcode_borders %>% 
                 st_drop_geometry() %>% 
                 dplyr::select(PLZ, Sum), by = c("Zipcode" = "PLZ")) %>%
    replace_na(list(n = 0, Sum = 0)) %>%  # Added replacing NA with 0 for Sum
    mutate(NormalizedCount = if_else(Sum == 0, 0, (n / Sum) * 100))  # handling division by zero
  return(data)
}

# Function to calculate percentage changes
percentage_changes <- function(before, during, after) {
  data <- before %>%
    dplyr::select(-n, -NormalizedCount) %>%
    mutate(PercentageChangeDuring = (during$NormalizedCount - before$NormalizedCount),
           PercentageChangeAfter = (after$NormalizedCount - before$NormalizedCount))
  return(data)
}

# Make sure to have the necessary data and libraries loaded before running the function

# Apply the functions
compute <- function(city_df, city_name) {
  # Split the data into three periods
  data_before <- city_df[city_df$Date < as.Date("2020-03-11"), ]
  data_during <- city_df[city_df$Date >= as.Date("2020-03-11") & city_df$Date < as.Date("2021-03-22"), ]
  data_after <- city_df[city_df$Date >= as.Date("2021-03-22"), ]

  before <- calculate_normalized_counts(data_before)
  during <- calculate_normalized_counts(data_during)
  after <- calculate_normalized_counts(data_after)

  changes <- percentage_changes(before, during, after)
}

# Execute for each city
computed_Zurich_df <- compute(Zurich_joined, "Zurich")

plot_maps <- function(data, city_name, bbox, city_coords) {
  plot_for_period <- function(data, change_column, title) {
    city_sf <- left_join(data, zipcode_borders, by = c("Zipcode" = "PLZ")) %>%
      st_as_sf() %>% 
      st_set_geometry(., "geometry") %>%
      st_crop(., bbox)

    labels = c("Very Negative", "Negative", "Neutral", "Positive", "Very Positive")
  
    # Create the tmap plot
    tm <- tm_shape(city_sf) +
          tm_fill(col = change_column, style = "quantile", 
                  palette= c( "#A6611A","#DFC27D","#F5F5F5","#80CDC1","#018571"),
                  title = paste0(city_name," - Change In Visitation Rates [%]"), legend.reverse = TRUE, n = 5) +
          tm_borders(col = "#cccccc", lwd = 0.1) +
          tm_shape(st_crop(zipcode_borders, bbox)) +
          tm_borders(col = "#cccccc", lwd = 0.1) +
          tm_shape(st_crop(canton_borders, bbox)) +
          tm_borders(col = "black") +
          tm_shape(city_coords) +
          tm_symbols(shape = 4, size = 0.3, col = "black") +
          tm_shape(st_crop(lakes, bbox)) +
          tm_fill(col = "#88CCEE") +
          tm_borders(col = "#cccccc", lwd = 0.1) +
          tm_layout(title = paste0(title),
                    frame = TRUE,
                    legend.position = c("left", "top"),
                    legend.text.size = 0.6,
                    legend.title.size = 0.6,
                    inner.margins = 0.1,
                    main.title.size = 2,
                    main.title.fontface = "italic", 
                    main.title.fontfamily = "sans") +
          tm_scale_bar(position = c("right", "bottom"), text.size = 0.5)
    
    # Print the map
    print(tm)
  }

  plot_for_period(data, "PercentageChangeDuring", "During Pandemic")
  plot_for_period(data, "PercentageChangeAfter", "After Pandemic")
}

plot_maps(computed_Zurich_df, "Zurich", zurich_box, zurich_sf)

```

#### Difference Visitations Geneva (GE)

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Function to compute normalized counts
calculate_normalized_counts <- function(data) {
  data <- data %>%
    group_by(Zipcode) %>%
    summarise(n = n()) %>%
    ungroup() %>%
    right_join(zipcode_borders %>% 
                 st_drop_geometry() %>% 
                 dplyr::select(PLZ, Sum), by = c("Zipcode" = "PLZ")) %>%
    replace_na(list(n = 0, Sum = 0)) %>%  # Added replacing NA with 0 for Sum
    mutate(NormalizedCount = if_else(Sum == 0, 0, (n / Sum) * 100))  # handling division by zero
  return(data)
}

# Function to calculate percentage changes
percentage_changes <- function(before, during, after) {
  data <- before %>%
    dplyr::select(-n, -NormalizedCount) %>%
    mutate(PercentageChangeDuring = (during$NormalizedCount - before$NormalizedCount),
           PercentageChangeAfter = (after$NormalizedCount - before$NormalizedCount)) 
  
  data$PercentageChangeDuring <- as.numeric(data$PercentageChangeDuring)
  data$PercentageChangeAfter <- as.numeric(data$PercentageChangeAfter)
  return(data)
}

# Apply the functions
compute <- function(city_df, city_name) {
  # Split the data into three periods
  data_before <- city_df[city_df$Date < as.Date("2020-03-11"), ]
  data_during <- city_df[city_df$Date >= as.Date("2020-03-11") & city_df$Date < as.Date("2021-03-22"), ]
  data_after <- city_df[city_df$Date >= as.Date("2021-03-22"), ]

  before <- calculate_normalized_counts(data_before)
  during <- calculate_normalized_counts(data_during)
  after <- calculate_normalized_counts(data_after)

  changes <- percentage_changes(before, during, after)
}

# Execute for each city
computed_Zurich_df <- compute(Zurich_joined, "Zurich")
computed_Bellinzona_df <- compute(Bellinzona_joined, "Bellinzona")
computed_Geneva_df <- compute(Geneva_joined, "Geneva")

plot_maps <- function(data, city_name, bbox, city_coords) {
  plot_for_period <- function(data, change_column, title) {
    city_sf <- left_join(data, zipcode_borders, by = c("Zipcode" = "PLZ")) %>%
      st_as_sf() %>% 
      st_set_geometry(., "geometry") %>%
      st_crop(., bbox)
    
    

    # Create the tmap plot
    tm <- tm_shape(city_sf) +
          tm_fill(col = change_column, style = "quantile", n = 5, 
                  palette= c( "#A6611A","#DFC27D","#F5F5F5","#80CDC1","#018571"),
                  title = paste0(city_name," - Change In Visitation Rates [%]")) +
          tm_borders(col = "#cccccc", lwd = 0.1) +
          tm_shape(st_crop(zipcode_borders, bbox)) +
          tm_borders(col = "#cccccc", lwd = 0.1) +
          tm_shape(st_crop(canton_borders, bbox)) +
          tm_borders(col = "black") +
          tm_shape(city_coords) +
          tm_symbols(shape = 4, size = 0.3, col = "black") +
          tm_shape(st_crop(lakes, bbox)) +
          tm_fill(col = "#88CCEE") +
          tm_borders(col = "#cccccc", lwd = 0.1) +
          tm_layout(title = paste0(title),
                    frame = TRUE,
                    legend.position = c("left", "top"),
                    legend.text.size = 0.6,
                    legend.title.size = 0.6,
                    inner.margins = 0.1,
                    main.title.size = 2,
                    main.title.fontface = "italic", 
                    main.title.fontfamily = "sans") +
          tm_scale_bar(position = c("right", "bottom"), text.size = 0.5)
    
    # Print the map
    print(tm)
  }

  plot_for_period(data, "PercentageChangeDuring", "During Pandemic")
  plot_for_period(data, "PercentageChangeAfter", "After Pandemic")
}

plot_maps(computed_Geneva_df, "Geneva", geneva_box, geneva_sf)

```

#### Difference Visitations Ticino (TI)

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Function to compute normalized counts
calculate_normalized_counts <- function(data) {
  data <- data %>%
    group_by(Zipcode) %>%
    summarise(n = n()) %>%
    ungroup() %>%
    right_join(zipcode_borders %>% 
                 st_drop_geometry() %>% 
                 dplyr::select(PLZ, Sum), by = c("Zipcode" = "PLZ")) %>%
    replace_na(list(n = 0, Sum = 0)) %>%  # Added replacing NA with 0 for Sum
    mutate(NormalizedCount = if_else(Sum == 0, 0, (n / Sum) * 100))  # handling division by zero
  return(data)
}

# Function to calculate percentage changes
percentage_changes <- function(before, during, after) {
  data <- before %>%
    dplyr::select(-n, -NormalizedCount) %>%
    mutate(PercentageChangeDuring = (during$NormalizedCount - before$NormalizedCount),
           PercentageChangeAfter = (after$NormalizedCount - before$NormalizedCount))
  return(data)
}

# Make sure to have the necessary data and libraries loaded before running the function

# Apply the functions
compute <- function(city_df, city_name) {
  # Split the data into three periods
  data_before <- city_df[city_df$Date < as.Date("2020-03-11"), ]
  data_during <- city_df[city_df$Date >= as.Date("2020-03-11") & city_df$Date < as.Date("2021-03-22"), ]
  data_after <- city_df[city_df$Date >= as.Date("2021-03-22"), ]

  before <- calculate_normalized_counts(data_before)
  during <- calculate_normalized_counts(data_during)
  after <- calculate_normalized_counts(data_after)

  changes <- percentage_changes(before, during, after)
}

# Execute for each city
computed_Zurich_df <- compute(Zurich_joined, "Zurich")
computed_Bellinzona_df <- compute(Bellinzona_joined, "Bellinzona")
computed_Geneva_df <- compute(Geneva_joined, "Geneva")

plot_maps <- function(data, city_name, bbox, city_coords) {
  plot_for_period <- function(data, change_column, title) {
    city_sf <- left_join(data, zipcode_borders, by = c("Zipcode" = "PLZ")) %>%
      st_as_sf() %>% 
      st_set_geometry(., "geometry") %>%
      st_crop(., bbox)

    # Create the tmap plot
    tm <- tm_shape(city_sf) +
          tm_fill(col = change_column, style = "quantile", n = 5, 
                  palette= c( "#A6611A","#DFC27D","#F5F5F5","#80CDC1","#018571"),
                  title = paste0(city_name," - Change In Visitation Rates [%]")) +
          tm_borders(col = "#cccccc", lwd = 0.1) +
          tm_shape(st_crop(zipcode_borders, bbox)) +
          tm_borders(col = "#cccccc", lwd = 0.1) +
          tm_shape(st_crop(canton_borders, bbox)) +
          tm_borders(col = "black") +
          tm_shape(city_coords) +
          tm_symbols(shape = 4, size = 0.3, col = "black") +
          tm_shape(st_crop(lakes, bbox)) +
          tm_fill(col = "#88CCEE") +
          tm_borders(col = "#cccccc", lwd = 0.1) +
          tm_layout(title = paste0(title),
                    frame = TRUE,
                    legend.position = c(0.65,0.1),
                    legend.text.size = 0.6,
                    legend.title.size = 0.6,
                    inner.margins = 0.1,
                    main.title.size = 2,
                    main.title.fontface = "italic", 
                    main.title.fontfamily = "sans") +
          tm_scale_bar(position = c("right", "bottom"), text.size = 0.5)
    
    # Print the map
    print(tm)
  }

  plot_for_period(data, "PercentageChangeDuring", "During Pandemic")
  plot_for_period(data, "PercentageChangeAfter", "After Pandemic")
}

plot_maps(computed_Bellinzona_df, "Bellinzona", bellinzona_box, bellinzona_sf)

```


